#### Overview of CNV data

```{r, eval=T, message=F}
library(karyoploteR)
```

```{r}
## Filter out gains vs del
gain=which(AnnotCNV2$Segment_Mean>=paramfile$CNVfcHigh)
homloss=which(AnnotCNV$Segment_Mean<=paramfile$CNVfcLow)
```


```{r,fig.height=6, message=F}
gainMat <- GRanges(seqnames=AnnotCNV$chr[gain], ranges=IRanges(start=AnnotCNV$start[gain],
                      end=AnnotCNV$end[gain]), AF=AnnotCNV$Segment_Mean[gain])

if (length(gainMat)>0){
  gainMat$AFcol=brewer.pal(5, "Reds")[cut(gainMat$AF, c(0,  2, 6, 20, 100))]
}
  
#gainMat$AFcol=ifelse(gainMat$path!="", "#67000d", gainMat$AFcol)

# hetlossMat <-  GRanges(seqnames=paste0("chr",AnnotCNV[hetloss, 2]), ranges=IRanges(start=AnnotCNV[hetloss, 3], end=AnnotCNV[hetloss, 4]), path=AnnotCNV$Psource[hetloss],AF=ifelse(is.na(AnnotCNV$AF[hetloss]), 1, 1-AnnotCNV$AF[hetloss]))
# 
# hetlossMat$AFcol=ifelse(hetlossMat$path!="", "#006d2c", hetlossMat$AFcol)

homlossMat<- GRanges(seqnames=AnnotCNV$chr[homloss], ranges=IRanges(start=AnnotCNV$start[homloss],
                      end=AnnotCNV$end[homloss]), AF=AnnotCNV$Segment_Mean[homloss]) 

if (length(homlossMat)>0){
 homlossMat$AFcol=brewer.pal(5, "Greens")[cut(homlossMat$AF, c(0,  -2, -6, -20,-100))]
}


UniqueGenesA=unique(unlist(strsplit(AnnotCNV2$GenesOfInterest[c(gain, homloss)], ",")))
UniqueGenesA=gsub(",","", UniqueGenesA)
UniqueGenesB=unique(unlist(strsplit(AnnotCNV2$Cosmic[c(gain,homloss)], ", ")))
UniqueGenesC=AnnotCNV2$genes[grep(data$TreatmentKeywords, AnnotCNV2$GenesOfInterest)]
Tx3=na.omit(unique(c(UniqueGenesA, UniqueGenesB, UniqueGenesC)))
Tx3=setdiff(Tx3, data$TreatmentKeywords)

 if (length(Tx3)>0){
 genes=genesAll[na.omit(match(Tx3, genesAll$hgnc_symbol))]
  }

kp <- plotKaryotype(chromosomes=c("autosomal"), genome="hg38",plot.type=2)
ax=tryCatch({kpPlotRegions(kp, gainMat, col=gainMat$AFcol,data.panel = 1)}, error=function(e){NULL})
ax=tryCatch({kpPlotRegions(kp, homlossMat, col=homlossMat$AFcol,data.panel = 2)}, error=function(e){NULL})
ax=tryCatch({kpPlotMarkers(kp, data=genes, labels=genes$hgnc_symbol, text.orientation = "horizontal", r1=0.75, cex=0.5, adjust.label.position = FALSE)}, error=function(e){NULL})

```

#### Genes/Pathways of Interest

The following plot shows regions of gains or losses, colored by:

* <span style="color: red;"> Cosmic Cancer Gene (Tier 1 or 2 oncogene or tumor suppressor gene) </span>
* <span style="color: blue;"> Impacts the pathway of interest: `r data$TreatmentKeywords`, either through MSigDB annotation or user-defined gene list </span>
* <span style="color: purple;"> Gene is both in Cosmic List and is a gene of interest list in `r data$TreatmentKeywords` pathway </span>


```{r, fig.height=3.5}

chrNames=c(paste("chr", c(1:22), sep=""), "chrX", "chrY")

gList=genes$hgnc_symbol[which(seqnames(genes)%in%chrNames)]

lx1split=strsplit(AnnotCNV2$genes, ",")

lx1splitLength=sapply(lx1split, length)

lx1=which(lx1split%in%gList)

temp1=AnnotCNV2[lx1, c("chr", "start", "end","Segment_Mean", "Segment_Call", "GenesOfInterest", "Cosmic", "genes", "GTex", "Pathways")]
temp1$GenesOfInterest[grep(data$TreatmentKeywords, temp1$GenesOfInterest)]=temp1$genes[grep(data$TreatmentKeywords, temp1$GenesOfInterest)]

ContRun=ifelse(nrow(temp1)>1, T, F)
```


```{r, eval=ContRun}

tx2=grep(",", temp1$GenesOfInterest)

if (length(tx2)>0){
  Input2=strsplit(temp1$GenesOfInterest[tx2], ",") 
  lx3=sapply(Input2, length)
  tempMat=temp1[tx2, ]
  tempMat2=tempMat[rep(seq_len(nrow(tempMat)), times = lx3), ]
  tempMat2$GenesOfInterest=unlist(Input2)
  temp1=rbind(temp1[-tx2, ], tempMat2)
}

tx3=grep(",", temp1$Cosmic)

if (length(tx3)>0){
  Input2=strsplit(temp1$GenesOfInterest[tx3], ",") 
  lx3=sapply(Input2, length)
  tempMat=temp1[tx3, ]
  tempMat2=tempMat[rep(seq_len(nrow(tempMat)), times = lx3), ]
  tempMat2$GenesOfInterest=unlist(Input2)
  temp1=rbind(temp1[-tx3, ], tempMat2)
}

temp1=unique(temp1)
#temp1$Gene=ifelse(temp1$GenesOfInterest=="", temp1$Cosmic, ifelse(temp1$Cosmic=="", temp1$GenesOfInterest, paste(temp1$GenesOfInterest, temp1$Cosmic)))
# temp1$Gene=gsub(paste0(data$TreatmentKeywords), "", temp1$Gene)
# temp1$Gene=gsub(" ", "", temp1$Gene)
#temp1$Gene[which(temp1$Gene=="")]=NA
temp1$Col=ifelse((temp1$Cosmic!=""&temp1$GenesOfInterest!=""),"purple", ifelse(temp1$Cosmic!="", "red", "blue") )


#temp1$chr=factor(temp1$chr, levels=c(1:22, "X", "Y"))
temp1=temp1[order(temp1$chr,temp1$start), ]

# tempx=by(temp1$CN, temp1$Gene_name, mean)
# tempx2=stack(round(tempx))
# 
#  checkdup=which(duplicated(temp1[ ,c(4:7)]))
#  if (length(checkdup)>0){
#    temp2=temp1[-which(duplicated(temp1[ ,c(4:7)])), ]
#    temp2$CN=(tempx2$values[ match(temp2$Gene_name, tempx2$ind)])
#    #temp2$CN[which(temp2$CN==2)]=1
#    temp2$CN=factor(temp2$CN)
#  } else {
#    temp2=temp1
#  }


temp1$CN=cut(temp1$Segment_Mean, breaks=c(-100,-12,-6,-3 ,paramfile$CNVfcLow, paramfile$CNVfcHigh, 3, 6, 12, 100))
rm1=which(!is.na(temp1$CN))
temp2=temp1[rm1, ]

colB=temp2$Col

ggplot(temp2, aes(x=genes, y=1, fill=CN))+geom_tile()+theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())+scale_fill_manual(values = brewer.pal(9, "RdBu")[9:1])+expand_limits(y = 0.25)+geom_text(aes(colour = colB, label = genes), y = 0.35, angle=90)+facet_grid(~chr, space="free", scales="free")+scale_colour_manual(values = c("blue", "purple", "red"), guide = F)
```


#### Gene-specific Analysis

Genes which are Cancer-COSMIC related, or have relevance to the pathway of interest (`r data$TreatmentKeywords`)

* <span style="color: red;"> Gains or insertions (top) </span>
* <span style="color: blue;"> Deletions (Bottom) </span>
* The following CNV regions are filtered to retain those with a gain (log2FC > `r paramfile$CNVfcHigh`) or loss (log2FC < `r paramfile$CNVfcLow`) and a minimum number of probes:

**Multi-gene variants**

```{r}
temp1=temp1[ ,-which(colnames(temp1)=="CN")]
nxlength=lx1splitLength[lx1]
Mglist=which(nxlength>1)
MGexist=length(Mglist)>0
```

`r ifelse(MGexist==FALSE, print('There are no CNVs spanning multiple genes'), print('The CNVs spanning multiple genes are shown below:'))`

```{r, eval=MGexist}
DT::datatable(temp1[Mglist, ], rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 5,  buttons=c(I('colvis'),'csv', 'excel')))

```


**Gene level results**

```{r}
Mglist=which(nxlength==1)
T1b=temp1[Mglist, ]
DT::datatable(T1b, rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 5,  buttons=c(I('colvis'),'csv', 'excel')))

```
