#### Variant Summary

Summary of variants detected

```{r, eval=T, message=F}
D1=read.delim(data$SNVsummary)

VariantSummary=c("Total protein-associated non-synonymous variants ", "Total in Cancer Gene Census ",
             "Total associated with drug response ", "Total in pathways of interest ",
             "Total other pathogenic VUS ")
# write name to variable so we can evaluate intersections
Table1=cbind(VariantSummary, t(D1))
head(Table1)

kable(Table1, rownames = F)
```

#### Group A: Cancer Related

The following variants have been listed within the following sources:

* MSK's Oncokb Precision Oncology Database
* COSMIC's Cancer Gene Census (CGC): Tiers include Hallmark, Tier 1 & Tier 2 
* COSMIC's Cancer Mutation Census (Tiers 1-3) 

```{r, eval=T}
D2=read.delim(data$SNVcancerRes)

#BioVar=Xout$Func[ , (match(SearchTerms, colnames(Xout$Func)))]
#colnames(BioVar)=cNames
DT::datatable(D2[ ,c(1:6, 21, 20, 8,12,9, 13:19, 22)], rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))
```


#### Group B: Biologically relevant pathways

The following variants have been implicated in pathways related to `r data$TreatmentKeywords`.
Additionally, variants need to either have a documented ClinVar Significance, or have a CADD score greater than 20

```{r, eval=T}
D3=read.delim(data$SNVHallmark)

DT::datatable(D3[ ,c(1:6, 21, 20, 8,12,9, 13:19, 22)], rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))
```

#### Group C: Variants with Clinvar protective or drug response annotations

The following variants annotated with clinvar have reported the following:
* a potential protective effect
* can influence drug response

```{r, eval=T}
D4=read.delim(data$SNVdrugresponse)

DT::datatable(D4[ ,c(1:6, 20, 21, 8, 12:13,19,22)], rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))
```

#### Group D: Variants of unknown significance

The following variants:
* have a predicted CADD for for deleteriousness of 20+ (Top 1\% of deleteriousness)
* are present in the gnomAD database at an population frequency of 0.1 or less
* affect an defined functional domain of a protein

```{r, eval=T}
D5=read.delim(data$SNVVUS)

DT::datatable(D5[ ,c(1:6, 20, 21, 8, 12:13,19,22)], rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))
```



