#### Variant Summary

Summary of variants detected

```{r, eval=T, message=F}
# Read in the files generated from FilterVariants.R in order to print the following files
D1=read.delim(data$SNVsummary)
D2=read.delim(data$SNVcancerRes)
D3=read.delim(data$SNVHallmark)
D4=read.delim(data$SNVdrugresponse)
D5=read.delim(data$SNVVUS)
D6=read.delim(data$SNVACMG)

Variant.Type=c("Total coding non-synonymous variants", "Total in Cancer Gene Census",
             "Total associated with drug response", "Total in pathways of interest",
             "Total other pathogenic VUS", "Total ACMG variants")
# write name to variable so we can evaluate intersections
N=c( D1, nrow(D2), nrow(D3), nrow(D4), nrow(D5), nrow(D6))
Table1=cbind(Variant.Type,N)

kable(Table1, row.names = F)
```

#### TierA: Cancer Related

The following variants have been listed within the following sources:

* MSK's Oncokb Precision Oncology Database
* COSMIC's Cancer Gene Census (CGC): Tiers include Hallmark, Tier 1 & Tier 2 
* COSMIC's Cancer Mutation Census (Tiers 1-3) 
* Population Frequency Cutoff `r paramfile$TierAGnomad`
* Variants only in coding regions `r paramfile$TierAOnlyCoding`
* These genes include: `r sort(unique(D2$SYMBOL))`

```{r}
viewIdx=c("SYMBOL", "HGVSp",	"EXON",	"Consequence","ProteinDomain",
              "CMC.Oncogene","Pathogenicity", "gnomAD.AF","CancerGeneCensus.Tier", "UserGeneList","VAF","ClinVar.Sig", "Genotype", "CancerMutationCensus.Tier")
HideIdx=setdiff(1:ncol(D2), match(viewIdx, colnames(D2)))-1
DT::datatable(D2, rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 5,  buttons=c(I('colvis'),'csv', 'excel'), columnDefs = list(list(visible=FALSE, targets=HideIdx))))
```


#### Tier B: Biologically relevant pathways


The following variants:

* Have been implicated in pathways related to `r data$TreatmentKeywords`
* Population Frequency Cutoff `r paramfile$TierBGnomad`
* CADD score threshold `r paramfile$TierBCadd`
* Variants only in coding regions `r paramfile$TierBOnlyCoding`
* Is non-benign according to ClinVar OR Polyphen `r paramfile$TierBPathogenic`
* These genes include: `r sort(unique(D3$SYMBOL))`

```{r}
viewIdx=c("SYMBOL", "HGVSp","EXON",	"Consequence","ProteinDomain",
              "CMC.Oncogene","PolyPhen", "gnomAD.AF", "UserGeneList","VAF","ClinVar.Sig", "Genotype", "CancerMutationCensus.Tier", "HallmarkPathways")
HideIdx=setdiff(1:ncol(D3), match(viewIdx, colnames(D3)))-1
DT::datatable(D3, rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 10,  buttons=c(I('colvis'),'csv', 'excel'), columnDefs = list(list(visible=FALSE, targets=HideIdx))))

```

#### Tier C: Variants with Clinvar protective or drug response annotations


The following variants annotated with clinvar have reported the following:

* a potential protective effect
* can influence drug response
* These genes include: `r sort(unique(D4$SYMBOL))`

```{r}

viewIdx=c("SYMBOL","rsID", "HGVSp",	"EXON","ClinVar.Disease", "ClinVar.Sig", "ClinVar", "ProteinDomain")
HideIdx=setdiff(1:ncol(D4), match(viewIdx, colnames(D4)))-1
DT::datatable(D4, rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 10,  buttons=c(I('colvis'),'csv', 'excel'), columnDefs = list(list(visible=FALSE, targets=HideIdx))))

```

#### Tier D: Variants of unknown significance

The following variants:

* Population Frequency Cutoff `r paramfile$TierDGnomad`
* CADD score threshold `r paramfile$TierDCadd`
* Variants only in coding regions `r paramfile$TierDOnlyCoding`
* Is non-benign according to ClinVar OR Polyphen `r paramfile$TierDPathogenic`
* These genes include: `r sort(unique(D5$SYMBOL))`

```{r}
viewIdx=c("SYMBOL", "HGVSp",	"EXON", "ProteinDomain", "gnomAD.AF", "Pathogenicity", "HallmarkPathways")
HideIdx=setdiff(1:ncol(D5), match(viewIdx, colnames(D5)))-1
DT::datatable(D5, rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 10,  buttons=c(I('colvis'),'csv', 'excel'), columnDefs = list(list(visible=FALSE, targets=HideIdx))))
```

#### Tier E: ACMG variants


The following variants:

* have a variant in a ACMG listed gene 
* variant is predicted to be pathogenic or likely pathogenic by ClinVar
* These genes include: `r sort(unique(D6$SYMBOL))`

```{r}
viewIdx=c("SYMBOL", "HGVSp",	"EXON", "ProteinDomain", "gnomAD.AF", "Pathogenicity", "HallmarkPathways", "CMC.Oncogene", "ClinSig")
HideIdx=setdiff(1:ncol(D6), match(viewIdx, colnames(D6)))-1
DT::datatable(D6, rownames=F, filter = 'top', class='cell-border stripe',extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 10,  buttons=c(I('colvis'),'csv', 'excel'), columnDefs = list(list(visible=FALSE, targets=HideIdx))))
```


