#### Summary of variants detected

```{r, eval=T, message=F}


# write name to variable so we can evaluate intersections

Table1=cbind(c("Total coding load", "Total coding (omit HLA)","No. Actionable", "No. Biologically Relevant", "No. VUS", "TMB (mut/Mb)"), 
             Xout[[1]])
kable(Table1, rownames = F)
```

#### Potentially Actionable

The genes listed below are known driver events in cancer and therapies have been developed to target these genes.

```{r, eval=T}

SearchTerms=c("Hugo_Symbol", "HGVSg","HGVSp","cadd","t_VAF","MUTATION_EFFECT","Oncokb","DrugBank", "CGC_Cancer.Syndrome")

cNames=c("Gene",  "Mutation ", "Mutation (AA)","CADD", "Tumor VAF", "Effect", "OncoKB", "DrugBank", "GeneticSyndrome")
BioVar=Xout$Func[ , (match(SearchTerms, colnames(Xout$Func)))]
colnames(BioVar)=cNames

if (nrow(BioVar)>0){
BioVar$TCGAlink=paste0("<a href='", sprintf("https://www.cbioportal.org/results/mutations?case_set_id=all&gene_list=%s&cancer_study_list=5c8a7d55e4b046111fee2296", BioVar$Gene), "' target='_blank'>", BioVar$Gene, "</a>")
BioVar$Onockb=paste0("<a href='https://www.oncokb.org/gene/", BioVar$Gene, "' target='_blank'>", BioVar$Gene, "</a>")

} 

DT::datatable(BioVar, escape=F,rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))

```

#### Biologically relevant

There is a substantial body of evidence supporting the following genes in cancer, and these mutations are predicted to have a cadd score > 20

```{r, eval=T}
SearchTerms=c("Hugo_Symbol", "HGVSg", "HGVSp","cadd","t_VAF","Oncokb","DrugBank", "CGC_Cancer.Syndrome")

cNames=c("Gene","Mutation", "Mutation (AA)", "CADD", "Tumor VAF", "OncoKB", "DrugBank", "GeneticSyndrome")


BioVar=Xout$Prob[ , (match(SearchTerms, colnames(Xout$Prob)))]
if (nrow(BioVar)>0){
colnames(BioVar)=cNames
BioVar$TCGAlink=paste0("<a href='", sprintf("https://www.cbioportal.org/results/mutations?case_set_id=all&gene_list=%s&cancer_study_list=5c8a7d55e4b046111fee2296", BioVar$Gene), "' target='_blank'>", BioVar$Gene, "</a>")
BioVar$Onockb=paste0("<a href='https://www.oncokb.org/gene/", BioVar$Gene, "' target='_blank'>", BioVar$Gene, "</a>")
}
DT::datatable(BioVar, escape=F, rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))
```

#### Variants of unknown significance

The following genes are predicted to have a deleterious effect (cadd score>20), but uncertain involvement in cancer.


```{r}
BioVar=Xout$VUS[ , (match(SearchTerms, colnames(Xout$VUS)))]
colnames(BioVar)=cNames
BioVar$TCGAlink=paste0("<a href='", sprintf("https://www.cbioportal.org/results/mutations?case_set_id=all&gene_list=%s&cancer_study_list=5c8a7d55e4b046111fee2296", BioVar$Gene), "' target='_blank'>", BioVar$Gene, "</a>")
DT::datatable(BioVar, rownames=F,escape=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE, pageLength = 15, buttons=c('csv', 'excel')))

```

#### Other Variants

```{r}
BioVar=Xout$Other[ , (match(SearchTerms, colnames(Xout$Other)))]
colnames(BioVar)=cNames
DT::datatable(BioVar, rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scoller = TRUE,  buttons=c('csv', 'excel')))
```
