#### Overview of germline CNV data

[`r data$CNVplot`](Overview of tumour copy number profile)

```{r, eval=T, message=F}
library(karyoploteR)
dGenes=data$CNVfunco
AnnotCNV=read.delim(dGenes)
AnnotCNV2=AnnotCNV[which(AnnotCNV$Segment_Mean>=paramfile$CNVfcHigh | AnnotCNV$Segment_Mean<=paramfile$CNVfcLow), ]
```

#### Gene-specific Analysis

Genes which are Cancer-COSMIC related, or have relevance to the pathway of interest (`r data$TreatmentKeywords`)

TODO: create a script to load these CNVs and annotate with a COSMIC

* <span style="color: red;"> Gains or insertions (top) </span>
* <span style="color: blue;"> Deletions (Bottom) </span>
* The following CNV regions are filtered to retain those with a gain (log2FC > 1) or loss (log2FC < -1) and a minimum number of probes:

```{r}
cNames=c("Chr", "Start", "End", "No.Probes", "log2 ratio", "CALL", "call", "Genes")
colnames(A1)=cNames
DT::datatable(A1[xa, -6], rownames=F, class='cell-border stripe',
          extensions="Buttons", options=list(dom="Bfrtip",scroller=T,pageLength = 15, buttons=c('csv', 'excel')))

```